\noindent{\small Some excerpts from an Interview with Malaclypse the Younger by \textit{The Greater Metropolitan Yorba Linda Herald\-/News\-/Sun\-/Tribune\-/Journal\-/Dispatch\-/Post and San Francisco Discordian Society Cabal Bulletin and Intergalactic Report \& Pope Poop}...}

\index{Mal-2}

\begin{dialogue}
\small
\speak{Greater Poop} Are you really serious or what?
\speak{Mal-2} Sometimes I take humor seriously. Sometimes I take seriousness humorously. Either way it is irrelevant.
\vspace{1em}
\speak{GP} Maybe you are just crazy. 
\speak{M2} Indeed! But do not reject these teaching as false because I am crazy. The reason that I am crazy is because they are true.
\vspace{1em}
\speak{GP} Is Eris true? 
\speak{M2} Everything is true. 
\speak{GP} Even false things? 
\speak{M2} Even false things are true. 
\speak{GP} How can that be? 
\speak{M2} I don't know man, I didn't do it.
\vspace{1em}
\speak{GP} Why do you deal with so many negatives? 
\speak{M2} To dissolve them. 
\speak{GP} Will you develop that point? 
\speak{M2} No.
\vspace{1em}
\speak{GP} Is there an essential meaning behind POEE? 
\speak{M2} There is a Zen Story about a student who asked a Master to explain the meaning of Buddhism. The Master's reply was ``Three pounds of flax.'' 
\speak{GP} Is that the answer to my question? 
\speak{M2} No, of course not. That is just illustrative. The answer to your question is FIVE TONS OF FLAX!
\end{dialogue}

\begin{textblock}{0.8}[0.5,0.5](0.5,0.05)
\Huge\noindent\textsf{\textbf{
s\kern-0.05em\lower0.1em\hbox{u}\kern-0.05em\hbox{s}\kern-0.05em\lower0.05em\hbox{\mturn{10}{p}}\kern-0.12em\lower0.05em\hbox{\mturn{-5}{e}}\kern-0.05em\lower0.05em\hbox{\mturn{-5}{n}}\kern-0.1em\hbox{d}\kern-0.07em\lower0.08em\hbox{\mturn{-5}{e}}\kern-0.05em\lower0.07em\hbox{d} \\
\hspace*{1.70em}\raisebox{0.5em}[0pt][0pt]{\mturn{-5}{a}\kern-0.07em\lower0.15em\hbox{\mturn{5}{n}}\kern-0.1em\hbox{n}\kern-0.08em\lower0.15em\hbox{\mturn{2}{i}}\kern-0.05em\lower0.19em\hbox{h}\kern-0.08em\lower0.15em\hbox{\mturn{2}{i}}\kern-0.05em\lower0.23em\hbox{\mturn{3}{l}}\kern-0.07em\lower0.10em\hbox{\mturn{-5}{a}}\kern-0.07em\hbox{t}\kern-0.05em\lower0.1em\hbox{\mturn{2}{i}}\kern-0.05em\hbox{o}\kern-0.05em\lower-0.2em\hbox{\mturn{-2}{n}}}
}}
\end{textblock}
